High-Dimensional Regularized Discriminant Analysis

### 2017-10-17 reports/paper-hdrda.Rnw
changes for T&F template

\usepackage{graphicx, mathtools, amssymb, bm, amsthm}
\usepackage{algorithm2e, url}

@@

% natbib.sty for citation and bibliography support
\usepackage[numbers,sort&compress]{natbib}
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\makeatletter% @ becomes a letter
\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
\makeatother% @ becomes a symbol again

@@

%\articletype{ARTICLE TEMPLATE} % Specify the article type or omit as appropriate

@@

% \author{
% \name{John.~A. Ramey\textsuperscript{a}\thanks{CONTACT John.~A. Ramey. Email: johnramey@gmail.com}, Caleb~K. Stein\textsuperscript{b}, Phil~D. Young\textsuperscript{c}, and Dean~M. Young\textsuperscript{d}}
% \affil{\textsuperscript{a}Novi Labs, Austin, TX, USA; \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA; \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA; \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA;}
%}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
}

@@

% TODO: Are these codes needed?
% \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22
\begin{keywords}
Regularized discriminant analysis; High-dimensional classification; Covariance-matrix regularization; Singular value decomposition; Multivariate analysis; Dimension reduction
\end{keywords}

@@

Next, we establish that the matrix operations corresponding to the null space of
the pooled sample covariance matrix are redundant and can be discarded from the
\emph{HDRDA} decision rule without loss of classificatory information when we
apply reasoning similar to that of \cite{Ye:2006tq}. As a result, we achieve a
substantial reduction in dimension such that the matrix operations used in the
\emph{HDRDA} classifier are computationally linear in the number of features.
Furthermore, we demonstrate that the \emph{HDRDA} decision rule is invariant to
adjustments to the approximately $p - N$ zero eigenvalues, so that the decision
rule in the original feature space is equivalent to a decision rule in a lower
dimension, such that matrix inverses and determinants of relatively small
matrices can be rapidly computed. Finally, we show that several shrinkage
methods that are special cases of the \emph{HDRDA} classifier have no effect on
the approximately $p - N$ zero eigenvalues of the covariance-matrix estimators
when $p > N$. Such techniques include work from \cite{Srivastava:2007ww},
\cite{Rao:1971ul}, and other methods studied by \cite{Ramey:2013ji} and
\citet*{Xu:2009fl}.

@@

\subsubsection{\cite{Chiaretti:2004gq} Data Set}

@@

\subsubsection{\cite{Chowdary:2006kf} Data Set}

@@

\subsubsection{\cite{Nakayama:2007fl} Data Set}

@@

\subsubsection{\cite{Shipp:2002ka} Data Set}

@@

\subsubsection{\cite{Singh:2002fh} Data Set}

@@

\subsubsection{\cite{Tian:2003ht} Data Set}

@@

@@

xtable_out <- xtable(results_microarray,
                     caption=table_caption,
                     label='tab:microarray-results')
print(xtable_out, include.rownames=FALSE, sanitize.text.function = function(x) { x })
@

>>>>

\usepackage{graphicx, mathtools, amssymb, bm, amsthm}
\usepackage{algorithm2e, url}
\usepackage{setspace}

@@

% natbib.sty for citation and bibliography support
\usepackage[numbers,sort&compress]{natbib}
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\makeatletter% @ becomes a letter
\def\NAT@def@citea{\def\@citea{\NAT@separator}} % Suppress spaces between citations using natbib.sty
\makeatother % @ becomes a symbol again

@@

% Specify the article type or omit as appropriate
\articletype{Submission}

@@

\author{
\name{John A. Ramey\textsuperscript{a}\thanks{CONTACT John A. Ramey. Email: johnramey@gmail.com}, Caleb K. Stein\textsuperscript{b}, Phil D. Young\textsuperscript{c}, and Dean M. Young\textsuperscript{d}}
\affil{\textsuperscript{a}Novi Labs, Austin, TX, USA; \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA; \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA; \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA}
}

\maketitle

\doublespacing

@@

% TODO:
% 1. Word count
% 2. Update plots to TIFF format with correct parameters.
% 3. Are MSC codes needed?: \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22

\begin{keywords}
Regularized discriminant analysis; High-dimensional classification; Covariance-matrix regularization; Singular value decomposition; Multivariate analysis; Dimension reduction
\end{keywords}

@@

Next, we establish that the matrix operations corresponding to the null space of
the pooled sample covariance matrix are redundant and can be discarded from the
\emph{HDRDA} decision rule without loss of classificatory information when we
apply reasoning similar to that of \cite{Ye:2006tq}. As a result, we achieve a
substantial reduction in dimension such that the matrix operations used in the
\emph{HDRDA} classifier are computationally linear in the number of features.
Furthermore, we demonstrate that the \emph{HDRDA} decision rule is invariant to
adjustments to the approximately $p - N$ zero eigenvalues, so that the decision
rule in the original feature space is equivalent to a decision rule in a lower
dimension, such that matrix inverses and determinants of relatively small
matrices can be rapidly computed. Finally, we show that several shrinkage
methods that are special cases of the \emph{HDRDA} classifier have no effect on
the approximately $p - N$ zero eigenvalues of the covariance-matrix estimators
when $p > N$. Such techniques include work from \cite{Srivastava:2007ww},
\cite{Rao:1971ul}, and other methods studied by \cite{Ramey:2013ji} and
\cite{Xu:2009fl}.

@@

\subsubsection{Chiaretti Data Set}

@@

\subsubsection{Chowdary Data Set}

@@

\subsubsection{Nakayama Data Set}

@@

\subsubsection{Shipp Data Set}

@@

\subsubsection{Singh Data Set}

@@

\subsubsection{Tian Data Set}

@@

xtable_out <- xtable(results_microarray,
                     caption=table_caption,
                     label='tab:microarray-results')
print(xtable_out, include.rownames=FALSE, sanitize.text.function = function(x) { x },
      scalebox='0.85') # scales the table to fit the page
@

@@
